Summary

### 2015-10-29 inst/examples/summary.Rmd
ok

library(stringr)
library(dplyr)
library(ggplot2)

@@

missing <- 100*apply(df, 2, function (x) {mean(is.na(x))})
df2 <- data.frame(list(missing = missing, field = names(missing)))
df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
theme_set(theme_bw(15))
p <- ggplot(df2, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with data (%)")
print(p)
```

@@

## Publication

### Publication places

```{r city2, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/publication_place.csv"
print(paste("Complete counts in file:", f))
tmp <- write_xtable(df$publication_place, filename = f)
```

>>>>

library(stringr)
library(dplyr)
library(ggplot2)
ntop <- 20

@@

# Need to use this trick to have NAs for all data types
missing <- 100*apply(df, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
df2 <- data.frame(list(missing = missing, field = names(missing)))
df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
```

Percentage of non-NA entries among all documents in the preprocessed data (note that in some cases a significant fraction of this information is missing already in the raw data)

```{r missingb, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
theme_set(theme_bw(15))
p <- ggplot(df2, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with data (%)")
print(p)
```

Fields of special interest: real success percentage (proportion of successful conversions compared to non-NA entries in the original data):

```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
dfs <- df %>% select(author, publication_place, country, publication_year, published_from, published_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2, publisher)
success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))

# Compare the number of non-NA entries in preprocessed data to number
# of non-NA entries in the original data:
real.success <- c()
real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
real.success[["country"]] <- success$country/original.nonNA$publication_place
real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
real.success[["published_from"]] <- success$published_from/original.nonNA$publication_time
real.success[["published_till"]] <- success$published_till/original.nonNA$publication_time
real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
real.success[["area"]] <- success$area/original.nonNA$physical_dimension
real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
real.success[["author"]] <- success$author/original.nonNA$author
real.success[["paper"]] <- success$paper.consumption.km2/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 1), xlab = "Success rate (%)")
```

## Pagecounts

[Discarded page count data](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages-accepted-discarded.csv)

[Successfully converted page counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages-accepted.csv)

Compare gatherings and cm2 sizes as a quality check. This includes all data; the area has been estimated from the gatherings when dimension information was not available.

```{r summarysizecomp, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7}
dfs <- df %>% filter(!is.na(area) & !is.na(gatherings))
dfs <- dfs[, c("gatherings", "area")]
dfm <- melt(table(dfs))
names(dfm) <- c("gatherings", "area", "documents")
dfm$gatherings <- order_gatherings(dfm$gatherings)
p <- ggplot(dfm, aes(x = gatherings, y = area)) 
p <- p + scale_y_continuous(trans = "log2")
p <- p + geom_point(aes(size = documents))
p <- p + scale_size(trans="log10")
p <- p + ggtitle("Document size distribution: gatherings vs. cm2")
p <- p + xlab("Size (gatherings)")
p <- p + ylab("Size (cm2)")
p <- p + coord_flip()
print(p)
```

Compare gatherings and page counts.

```{r summarypagecomp, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
dfs <- select(df, pagecount, gatherings) 
dfs$pagecount <- as.numeric(gsub(" pages", "", dfs$pagecount))
dfs <- dfs %>% filter(!is.na(pagecount) & !is.na(gatherings))
dfg <- group_by(dfs, pagecount, gatherings) %>% tally()
names(dfg) <- c("pages", "gatherings", "documents")
dfg$gatherings <- order_gatherings(dfg$gatherings)
ylims <- range(dfg$pages)
p <- ggplot(dfg, aes(x = gatherings, y = pages)) 
n <- nchar(max(na.omit(table(dfg$pages))))
ylim <- ylim(ylims)
p <- p + scale_y_log10(breaks=10^(0:n))
p <- p + geom_point(aes(size = documents))
p <- p + scale_size(trans="log10")
p <- p + xlab("Size (gatherings)")
p <- p + ylab("Pages (original and estimated)")
p <- p + coord_flip()
print(p)
```

## Publication time

[Successfully converted publication times](publication-time-accepted.csv)

[Discarded publication times](publication-time-discarded.csv)

```{r publication_time, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
hist(df$publication_year, main = "Document frequencies over time")
```

## Publication places

[Successfully converted publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place.csv)

[Discarded publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_discarded.csv)

[Publication places missing country information](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_missingcountry.csv)

## Dimensions

[Successfully converted dimension info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/accepted_dimensions.csv)

[Discarded dimension info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/missing_dimensions.csv)

[Discarded gatherings info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/missing_gatherings.csv)

## Publisher

[Accepted publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_accepted.csv)

[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.csv)

We also have corporate info available ?

[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)

[Accepted author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.csv)

[Discarded author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.csv)

@@
